Drawing Math

### 2022-05-10 paper/Paper.tex
paper prog

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngleJ}[2]{{\theta^{#2}_{#1}}}
\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}
\newcommand{\digSumPeriodicNoJ}{\mathrm{digSumPeriodic}}
\newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}

@@

\subsection{Specifying the task ahead of us}
For our case, we consider $Comb, SU^j$ to all be memoryless (i.e.\ there output
is uniquely determined by the current input). So, we can simplify the overall question.
If, $\pmb{s}_i = \pmb{s}_{i + \ell T}$ for some $T \in \N$ and all $i \in \N$, then 
$\Delta p_{i} = \Delta p_{i + \ell T}$. So then,
$\Delta P_{i, i + \ell T} = \Delta P_{i, i + \ell' T}$ for all $\ell, \ell' \in \N$.
Thus, $T$ is a period of the change in position. We can thus
break down our problem into two parts:
\begin{enumerate}
  \item Finding the period, $T$, of the state $\pmb{s}$.
  \item Checking whether $\Delta P_{i, i + T} = 0$.
\end{enumerate}

\subsection{Some more restrictions on our problem}
We further restrict the problem by only considering the case where
$$
  Comb((., ., ., ., \theta^1), (., ., ., ., \theta^2), ..., (., ., ., ., \theta^k)) =
    \left(\combSingleTerm{1}, ..., \combSingleTerm{D}\right)
$$
where $\mathrm{incl}_d^j \in \set{0, 1}$ for $d \in [D]$ indicates whether to include a given
$x \in R$ determined by seed $j$ for position update in the $d$th dimension.

We will also let $\mathcal{S} = N^5$ where for $(n, d, b, \theta) \in \mathcal{S}$,
$n$ is the numerator of a rational in fraction form, $d$ is the denominator, 
$b$ is the base (i.e\. base 10, base 12, etc.), $i$ is the current time step,
and $\frac{2\theta}{b \pi}$ is an ``angle" associated with the state.
Moreover, we will only consider
$$
  SU^j(n, b, d, \theta) = (n, b, d, \theta + \mathrm{digit}(n, b, d, i) \mod b).
$$

@@

@@

@@

Moreover, define function $\digSumPeriodic \in \Z_b$
such that
% TODO: define T within the func from another func
% TODO: bettr defn
\begin{equation}
  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i)
\end{equation}

@@

\subsubsection{Closing along a single dimension}
Finally, to see if a shape will close,
we just need to find if equation \eqref{eq:singleDelta0} holds true for all dimensions.
First, let $A_d = \set{j \mid j \in [k] \; ; \inclIndic{d}{j} = 1}$
We can then see that
\begin{align*}
&\sum_{i = 1}^T \combSingleTerm{d}\\
&=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\right)^\inclIndic{d}{j}\\
&=2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
\end{align*}

@@

We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$ and $x, y \in \N$ where $y < \rationalPeriodTotal$,
\begin{align}
  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \notag \\
  &= \sum_{p = 0}^{(x- 1)\rationalPeriodTotal} \sum_{q=0}^{\rationalPeriodTotal - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + q)
    + \sum_{p = x \rationalPeriodTotal}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, p) \notag \\
    % ARGS::....
  \label{eq:angleBreakdown}
  &= x \cdot \digSumPeriodic + \sum_{p = x \rationalPeriodTotal}^{\rationalPeriodTotal + y}\mathrm{digit}(n, b, d, p) \notag \\
  &= x \cdot \digSumPeriodic + \sum_{p = 0}^{y}\mathrm{digit}(n, b, d, p)
\end{align}
because $\mathrm{digit}(n, b, d, x\rationalPeriodTotal + \ell) = \mathrm{digit}(n, b, d, \ell)$ for any $\ell \in \N$
by definition of periodicity.

Observe that 
\begin{align*}
 &\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right) \\
 =& \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} + \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) 
  + \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) + ... \\
  &+ \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} - ... - \seedAngleJ{p \rationalPeriodTotal + q}{d})
\end{align*}
which then equals
\begin{equation}
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right).
\end{equation}

Then, 
\begin{align*}
 &2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
 =& 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right)\\
 =&
  2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right)\\
 =&
  2^{-|A|} 
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
     \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right).
\end{align*}

@@

Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
\begin{equation}
\label{eq:wts01}  
  \eqWTSInnerProd
\end{equation}
always equals $0$ or $1$ for any choice of $\beta$.

Observe that 
\begin{align}
  \exp(\seedAngle{p \rationalPeriodTotal + q}I) &= \exp\left(p \cdot \digSumPeriodic +
    \sum_{\ell = p \rationalPeriodTotal}^{p \rationalPeriodTotal + q}\mathrm{digit}(n, b, d, \ell)\right) \tag{by equation \eqref{eq:angleBreakdown}} \\
    \label{eq:expBreakdown}
    &= \exp\left(p \cdot \digSumPeriodic\right) \exp\left(\sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)\right).
\end{align}

So then, by equation \eqref{eq:expBreakdown}, we get that
\begin{align}
&\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
    \seedAngle{p \rationalPeriodTotal + q}I = 
\right)\notag \\ 
\label{eq:decomposeExp}
=&
\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
    \cdot p \cdot
    \digSumPeriodic
\right)
\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
\right).
\end{align}

We then use \eqref{eq:decomposeExp} to show that \eqref{eq:wts01} equals
\begin{equation}
\label{eq:inner-outer-split}
  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \left[
    \exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)
  \left(
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
    \right)\right)\right].
\end{equation}

\subsubsection*{Case 1}
Observe that the inner sum,
$
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
  \exp\left(
      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
  \right)
$,
is invariant for all $p$ in equitation \eqref{eq:inner-outer-split}. So then,
let the inner sum equal $C_\beta \in \Z$.  Moreover, note that 
\begin{align*}
  &\exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)\\
  =& \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
\end{align*}
and that 
\begin{equation*}
  \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = \exp\left(0\right) = 1
\end{equation*}
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. Then, we can see that
$$
\prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = 1
$$
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$.

And so, because $\digSumPeriodic$ is a constant, we can conclude that
\begin{equation*}
 \exp\left(
      I \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right) 
\end{equation*}
is a $\totalOverRationalFrac^th$ root of unity iff $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$.

So, for $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$, we have that
\begin{align*}
  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1}
    \exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right) \\
    &= C \sum_{p = 0}^{\totalOverRationalFrac - 1}\exp\left(W_{\totalOverRationalFrac}^p\right) \\
    &= 0.
\end{align*}
where $W_{\totalOverRationalFrac}^p$ is the $\totalOverRationalFrac^{th}$ root of unity.

If $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} = 0$, then 
\begin{align*}
  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \exp(0) \\
  &= 1.
\end{align*}

@@

>>>>

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngleJ}[2]{{\theta^{#2}_{#1}}}
\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\numbToAngle}{\frac{2\pi}{b^j}}
\newcommand{\numbToAngleNoJ}[1]{\frac{2\pi}{b^{#1}}}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos\left(\numbToAngle \cdot \theta^j\right) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\sigma^j}
\newcommand{\digSumPeriodicNoJ}{{\sigma}}
\newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}
\newcommand{\changeTotalOneDim}{\Delta P_{0, T}^d}
\newcommand{\digit}{\mathrm{digit}}
\newcommand{\commonBase}{\pmb{b}}
\newcommand{\numbToCommon}{\frac{\commonBase}{b^j}}
\newcommand{\commonToAngle}{\frac{2\pi}{\commonBase}}

@@

\subsection{Specifying the task ahead of us}
For our case, we consider $Comb, SU_i^j$ to all be memoryless (i.e.\ there output
is uniquely determined by the current input). So, we can simplify the overall question.
If, $\pmb{s}_i = \pmb{s}_{i + \ell T}$ for some $T \in \N$ and all $i \in \N$, then 
$\Delta p_{i} = \Delta p_{i + \ell T}$. So then,
$\Delta P_{i, i + \ell T} = \Delta P_{i, i + \ell' T}$ for all $\ell, \ell' \in \N$.
Thus, $T$ is a period of the change in position. We can thus
break down our problem into two parts:
\begin{enumerate}
  \item Finding the period, $T$, of the state $\pmb{s}$.
  \item Checking whether $\Delta P_{i, i + T} = 0$.
\end{enumerate}

\subsection{Some more restrictions on our problem}
We further restrict the problem by only considering $\mathcal{S} = N^5$ where for $(n, d, b, \theta) \in \mathcal{S}$,
$n$ is the numerator of a rational in fraction form, $d$ is the denominator, 
$b$ is the base (i.e.\ base 10, base 12, etc.),
and $\frac{2\theta}{b \pi}$ is an ``angle" associated with the state.
Moreover, we will only consider
$$
  SU_i^j(n, b, d, \theta) = (n, b, d, \theta + \mathrm{digit}(n, b, d, i) \mod b).
$$

@@

Moreover, we consider the case where
$$
  Comb((., ., ., ., \theta^1), (., ., ., ., \theta^2), ..., (., ., ., ., \theta^k)) =
    \left(\combSingleTerm{1}, ..., \combSingleTerm{D}\right)
$$
where $\mathrm{incl}_d^j \in \set{0, 1}$ for $d \in [D]$ indicates whether to include a given
$x \in R$ determined by seed $j$ for position update in the $d$th dimension.

@@

Also, lets set 
$$\commonBase = \lcm{(n, b, d, \theta) \in \pmb{s}_0} b.$$
In other words,
$\commonBase$ can be thought of as a ``common base" among all seeds.

@@

Moreover, define $\digSumPeriodic \in \Z_b$
such that
% TODO: define T within the func from another func
% TODO: bettr defn
\begin{equation}
  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i).
\end{equation}
In other words, $\rationalPeriodTotal$ is the digital sum over one period.

@@

Before getting to the main result, we need to first prove the following lemma
\begin{lemma}{For all $j \in [k]$ and $x, y \in \N$ where $y < \rationalPeriodTotal$, we have that 
  $$
    \theta_{xT' + y}^j = x\cdot \digSumPeriodic + \sum_{q = 0}^y \digit(n, b, d, q)
  $$}
  \label{lemma:angleBreakdown}
  \begin{proof}
    We can then see that for $(n, b, d, \theta_{x\rationalPeriodTotal + y}^j) \in \pmb{s}_{x\rationalPeriodTotal + y}$,
    \begin{align*}
      \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \\
      &= \sum_{p = 0}^{(x- 1)\rationalPeriodTotal} \sum_{q=0}^{\rationalPeriodTotal - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + q)
          + \sum_{q = x \rationalPeriodTotal}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, q)\\
      &= x \cdot \digSumPeriodic + \sum_{q = x \rationalPeriodTotal}^{\rationalPeriodTotal + y}\mathrm{digit}(n, b, d, q)\\
      &= x \cdot \digSumPeriodic + \sum_{q = 0}^{y}\mathrm{digit}(n, b, d, q)
    \end{align*}
    because $\mathrm{digit}(n, b, d, x\rationalPeriodTotal + \ell) = \mathrm{digit}(n, b, d, \ell)$ for any $\ell \in \N$
    by definition of periodicity.
  \end{proof}
\end{lemma}

\subsubsection{Closing along a single dimension}
Let $\changeTotalOneDim$ be the change of position along dimension $d$
from timestep 0 to $T$.
We are now ready to determine if we ``close" along one dimension. I.e.\ does
$
\changeTotalOneDim = 0
$?

Define $A_d = \set{j \mid j \in [k] \; \text{and}\; \inclIndic{d}{j} = 1}$, in other words,
$A_d$ is the set of seeds which are included in determining the position along the $d$th dimension.
We can then see that
\begin{align*}
\changeTotalOneDim &=\sum_{i = 1}^T \combSingleTerm{d}\\
  &=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(\exp\left({\numbToAngle \seedAngle{i} I}\right) +  \exp\left(-\numbToAngle \seedAngle{i} I\right)\right)\right)^\inclIndic{d}{j}\\
  &= 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \prod_{j \in A_d} \left(
      \exp\left(\numbToAngle\seedAngle{p \rationalPeriodTotal + q} I\right) +  \exp\left(-\numbToAngle\seedAngle{p \rationalPeriodTotal + q} I\right)\right)
\end{align*}
by the Euler form of $\cos$.

@@

% TODO: not entirely correct with d
Next, observe that 
\begin{align*}
  &\prod_{j \in A_d} \left(
      \exp\left(\numbToAngle\seedAngle{p \rationalPeriodTotal + q} I\right) +  \exp\left(-\numbToAngle\seedAngle{p \rationalPeriodTotal + q} I\right)\right)\\
 =& 
  \exp(\numbToAngleNoJ{1}\seedAngleJ{p \rationalPeriodTotal + q}{1} + \numbToAngleNoJ{2}\seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \numbToAngleNoJ{d}\seedAngleJ{p \rationalPeriodTotal + q}{d}) 
  + \exp(\numbToAngleNoJ{1}\seedAngleJ{p \rationalPeriodTotal + q}{1} - \numbToAngleNoJ{2}\seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \numbToAngleNoJ{d}\seedAngleJ{p \rationalPeriodTotal + q}{d}) + ... \\
  &+ \exp(-\numbToAngleNoJ{1}\seedAngleJ{p \rationalPeriodTotal + q}{1} - \numbToAngleNoJ{2}\seedAngleJ{p \rationalPeriodTotal + q}{2} - ... - \numbToAngleNoJ{d}\seedAngleJ{p \rationalPeriodTotal + q}{d})
\end{align*}
which then equals
\begin{equation}
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
    \exp\left(
      	\commonToAngle I
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
          \numbToCommon \seedAngle{p \rationalPeriodTotal + q}
      \right)
\end{equation}
where $\beta$ can be though of as a bit string deciding whether the angle from seed
$j \in A_d$ is added to or subtracted from the exponent.

Then, we have that
% TODO: update with common base stuff...
\begin{align*}
 \changeTotalOneDim =&
  2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right)\\
 =&
  2^{-|A|} 
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
     \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right).
\end{align*}

@@

Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, define $Q$ such that
\begin{equation}
\label{eq:wts01}  
  Q = \eqWTSInnerProd.
\end{equation}
We will simplify $Q$ to show 2 distinct cases where $Q = 0$ for any choice of $\beta$.

Observe that 
\begin{align}
  \exp(\seedAngle{p \rationalPeriodTotal + q}I)
  &= \exp\left(p \cdot \digSumPeriodic +
    \numbToCommon \sum_{\ell = p \rationalPeriodTotal}^{p \rationalPeriodTotal + q}\mathrm{digit}(n^j, b^j, d^j, \ell)\right) \tag{by lemma \ref{lemma:angleBreakdown}} \\
    \label{eq:expBreakdown}
    &= \exp\left(p \cdot \digSumPeriodic\right) \exp\left(\numbToCommon \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)\right).
\end{align}

So then, by equation \eqref{eq:expBreakdown}, we get that
\begin{align}
&\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
    \seedAngle{p \rationalPeriodTotal + q}I
\right)\notag \\ 
\label{eq:decomposeExp}
=&
\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
    \cdot p \cdot
    \digSumPeriodic
\right)
\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}} \numbToCommon
      \sum_{\ell = 0}^{q}\mathrm{digit}(n^j, b^j, d^j, \ell).
\right).
\end{align}

We then use \eqref{eq:decomposeExp} to show that $Q$ equals
\begin{equation}
\label{eq:inner-outer-split}
  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \left[
    \exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)
  \left(
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}} \numbToCommon
          \sum_{\ell = 0}^{q}\mathrm{digit}(n^j, b^j, d^j, \ell)
    \right)\right)\right].
\end{equation}

\subsubsection*{Case 1}
Define
$$
  C_\beta = \sum_{q = 0}^{\rationalPeriodTotal - 1}
  \exp\left(
      \sum_{j \in A_d} -1 ^ {\beta_{(j)}} \numbToCommon
        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
  \right).
$$
Moreover, note that 
\begin{align*}
  &\exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)
  = \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
\end{align*}
and that 
\begin{equation*}
  \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = \exp\left(0\right) = 1
\end{equation*}
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. So, we can see that
$$
\prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = 1
$$
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$.

Because $\digSumPeriodic$ is a constant, we can conclude that
\begin{equation*}
 \exp\left(
      I \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right) 
\end{equation*}
is a $\totalOverRationalFrac^{th}$ root of unity iff 
$$\sum_{j \in A_d} -1 ^ {\beta_{(j)}}\digSumPeriodic \neq 0$$

So, for $\sum_{j \in A_d} -1 ^ {\beta_{(j)}}\digSumPeriodic \neq 0$, we have that
\begin{align*}
  \eqWTSInnerProd &= C_\beta \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1}
    \exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right) \\
    &= C_\beta \sum_{p = 0}^{\totalOverRationalFrac - 1}\exp\left(W_{\totalOverRationalFrac}^p\right) \\
    &= 0.
\end{align*}
where $W_{\totalOverRationalFrac}^p$ is the $\totalOverRationalFrac^{th}$ root of unity.

If $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \digSumPeriodic = 0$, then 
\begin{align*}
  \eqWTSInnerProd &= C_\beta \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \exp(0) \\
  &= C_\beta.
\end{align*}

@@

Said differently, let multinomial $m: \Z_{\commonBase} \rightarrow \Z_{\commonBase}$ be such that
\begin{equation*}
  m(x_1, x_2, ..., x_{|A_d|}) = \prod_{\beta \in \set{0, 1}^{|A_d|}} \left(\sum_{j \in A_d} -1^{\beta_j}AAA \right).
\end{equation*}
Then, if $m(\digSumPeriodicNoJ^1, \digSumPeriodicNoJ^2, ..., \digSumPeriodicNoJ^{|A_d|}) \neq 0$,
we know that the shape must close.

\subsubsection*{There does exist}
